---
title: "HW1"
subtitle: |
  | GR5072 - Modern Data Structures
  | Spring 2022 
author: "Zik"
date: "2/10/2022"
output:
  md_document:
    variant: markdown_github
  pdf_document: 
    toc: yes
  html_document:
    theme: journal
    toc: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Report: 
## This dataset contains information of subscribers who either subscribed or nor subscribed to a magazine. We are tasked to predict which segment of the customers are more likely to subscribe.


#table content
```{r}
data <- read.csv("/Users/zikangchen97/Desktop/Columbia/5072 QMSS/HW1/homework-1/src/hw_file/subscribed_data.csv")
df <- data.frame(data)
```

```{r}
str(df)
```


The three variables included in the dataset are:
1.Gender of the user 1 being female and 0 being male.
2.Age of the user. This variable takes on numerics value
3.A binary variabel indicating whether the user subscribed to the magazine or not


## Including Plots
```{r}
library(ggplot2)
ggplot(data = df, aes(x=Age, y=Subscribe)) + 
  geom_bar(stat = "identity") + ggtitle("Number of Subcription by Age")
```

```{r}
ggplot(data = df, aes(x=Gender, y=Subscribe)) + 
  geom_bar(stat = "identity") + ggtitle("Number of Subcription by Gender")
```

Conclusion:
1. As age increases, the subscription rate decreases among subscribers. People from the age 20-32 accounts for the majority of the subscriptions.
2. Female users are more likely to subscribe to the magazine than male users.






Credits and Reference Link: "https://github.com/bonheurgirl/Machine-Learning-R/blob/master/2.Predict%20Magazine%20Subscription%20Behavior%20-%20Logistic%20Regression.R"


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
